SFJ: An implementation of Semantic Featherweight Java

### 2020-02-19 conference/paper.tex
add algorithms of checking type trees and creating relation

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{verbatim}
boolean resolutionOccured = false
do 
    for each class that is unresolved:
        boolean resolved = true

        for each field that is a class type:
            if class type is not resolved 
                resolved = false

        if resolved == true
            set class to be resolved
            resolutionOccured = true
while resolutionOccured == true

if not all classes are resolved
    program contains invalid type definition
\end{verbatim}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath}
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{verbatim}
boolean resolutionOccured = false
do 
    for class that is unresolved:
        boolean resolved = true

        for field that contains a class type:
            if class type is not resolved 
                resolved = false

        if resolved is true
            set class to be resolved
            resolutionOccured = true
while resolutionOccured is true

if all classes are not resolved
    program contains invalid type definition
\end{verbatim}

Given that we now know that all the types in the program are valid, we can create the subtyping 
relation which will be a map of types to a set of its subtypes. For every program, we assume the 
initial subtyping relation for all of our basic types. We would like to highlight that Int is not
a subtype of Float as it cannot represent the whole domain of Int accurately therefore the domain is 
not fully contained in Float. Similarly so for Double and Long.

\begin{flalign*}
    Boolean &= \left\{Boolean \right\} &\\
    Double  &= \left\{Double, Float, Int, Short, Byte\right\} &\\
    Float &= \left\{Float, Short, Byte\right\} &\\
    Long &= \left\{Long, Int, Short, Byte\right\} &\\
    Int &= \left\{Int, Short, Byte\right\} &\\
    Short &= \left\{Short, Byte\right\} &\\
    Byte &= \left\{Byte\right\} & 
\end{flalign*}

Knowing that all our types are finite trees with leaves as constants and given this initial
relation, we can now confidently create a subtyping relation for all class types using the following
algorithm.

\begin{verbatim}
function generateRelation(classes):
    List<class> untyped = []

    for class in classes:
        if addClass(class) is false:
            untyped.add(class)

    if untyped is not []:
        generateRelation(untyped)

function addClass(class):
    for existing class type in relation:
        if tryAddSubtype(class, existingClass) is false:
            return false

        tryAddSubtype(existingClass, class)

        add class to its own subtype relation

function tryAddSubtype(class, other):
    boolean flag = true

    for field in class:
        if field contains type not in relation:
            return false

        if other does not have field:
            flag = false
        else:
            if other.field.types not fully contains field.types:
                flag = false

    for method in class:
        if method contains type not in relation:
            return false

        if other does not have method:
            flag = false
        else:
            if other.method.types not fully contains method.types:
                flag = false

    if flag == true:
        add class to other subtype relation
\end{verbatim}
